DOM bridges and barriers: systematic review and survey

### 2025-10-15 reports/draft_results.qmd
update results doc

### Result 2.3: Heat maps of theme co-occurence

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9
#| fig-height: 5
#| fig-align: center

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9
#| fig-height: 10
#| fig-align: center
consv <- codes_LU %>%
  gather(col, consv_topic, reason1:reason3) %>%
  gather(test, fishery_channel, fishery_or_channel1:fishery_or_channel4) %>%
  select(c(consv_topic, fishery_channel)) %>%
  mutate(consv_bin = paste0(consv_topic, " - ", fishery_channel))

>>>>

### Result 2.2: Heat maps of theme co-occurence

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 10
#| fig-height: 4
#| fig-align: center

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| fig-width: 9
#| fig-height: 12
#| fig-align: center
consv <- codes_LU %>%
  gather(col, consv_topic, reason1:reason3) %>%
  gather(test, fishery_channel, fishery_or_channel1:fishery_or_channel4) %>%
  select(c(consv_topic, fishery_channel)) %>%
  mutate(consv_bin = paste0(consv_topic, " - ", fishery_channel))
